---
title: "Water Women and Fisheries, SESYNC"
output: ioslides_presentation
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Water, Women, and Fisheries

Addressing two ecological realities impacting human health at the world’s largest tropical lake, Lake Victoria

- Jessica Corman
- Amber Roegner


Thanks to our coaches, Elizabeth and Mary!

## Lake Victoria

- Largest tropical lake (68,800 km^2^)
- Eutrophic
- Largest freshwater fishery (>500,000 tonnes yr^-1^)

## Winam Gulf

- Drinking water source for Kenya
- Population growth rates >3 %
- 30% of pollution to Lake Victoria 
- Water quality risks:

      + Nutrients
      + Cyanotoxins
      + E. coli, coliforms
      + Water hyacinth


## Research Questions
- Q1: Do perceptions of lake “water quality” correlate with ecological trends (spatial, variability,
temporal)?

- Q2: Do perceptions of lake “water quality” influence behavior or decision-making process
about ecosystem services? 

- Q3: Does intervention X change “water quality” locally (overall or variability in water quality)? If so, how?

- Q4: Does intervention X change individual perception of water quality? Does intervention X
change fisher or household behavior or decision-making process?


## Research Success

### Github site 
<https://github.com/afroegner/WWF_Victoria>


## Study sites in Winam Gulf
Combination of ecological and social data
```{r echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
source("code/DataPrep_SiteInfo.R")

library(ggmap)

# Map of Winam Gulf with all sites
bbox <- c(left=34,bottom=-0.6,right=34.9,top=0)
g <- ggmap(get_stamenmap(bbox, zoom=11, maptype="toner-lite"))
g +  geom_point(data=Lake_Sites,
                aes(x=Longitude, y=Latitude, color=Location), size=3, alpha=0.95) +
  geom_point(data=Communities,
             aes(x=Longitude, y=Latitude), alpha=0.5, color="black") +
  geom_hline(yintercept = 0, color = "black") +
  geom_vline(xintercept = 34.9, color="black") +
  theme_classic(12) 
```


## Q1. How do perceptions of lake “water quality” correlate with ecological trends?

- Comparison of surveys from communities with corresponding lake water quality information

## Preliminary exploration

```{r echo=FALSE, warning=FALSE, cache=TRUE, message=FALSE}
source(file = 'code/DataAnalysis_CorrelationWQbySurveys.R')
```

## Exploration of water quality across sites

```{r echo=TRUE, warning=FALSE, cache=TRUE, message=FALSE}
library(tidyverse)

lake_WQ <- read.csv("data_out/lake_WQ.csv")

# Compare water quality across sites and variables
names.WQ <- c("chloroa.µg_L", "TN.µgN_L", "Nitrates.µgN_L", "Ammonium.µgN_L",
              "TP.µgP_L", "SRP.µgP_L", "coliforms.MPN_100ml", 
              "ecoli.MPN_100ml", "totalMC.ug_L")

# Visualize data
# lake_WQ %>%
#  select(site, names.WQ) %>%
#  gather(key=variable, value = value, -site) %>%
#  ggplot(aes(x=site, y=value)) + 
#    geom_boxplot() + 
#    facet_wrap(~variable, scales="free")
```

## Exploration of water quality across sites

```{r echo=FALSE, warning=FALSE, cache=TRUE, message=FALSE}
library(tidyverse)

lake_WQ <- read.csv("data_out/lake_WQ.csv")

# Compare water quality across sites and variables
names.WQ <- c("chloroa.µg_L", "TN.µgN_L", "Nitrates.µgN_L", "Ammonium.µgN_L",
              "TP.µgP_L", "SRP.µgP_L", "coliforms.MPN_100ml", 
              "ecoli.MPN_100ml", "totalMC.ug_L")

# Visualize data
lake_WQ %>%
  select(site, names.WQ) %>%
  gather(key=variable, value = value, -site) %>%
  ggplot(aes(x=site, y=value)) + 
    geom_boxplot() + 
    facet_wrap(~variable, scales="free") +
  theme_bw(12)
```

## Exploration of water quality across Winam Gulf

```{r echo=FALSE, warning=FALSE, cache=TRUE, message=FALSE}
littoral_raw <- read.csv("/nfs/waterwomenfisheries-data/community_intake_cyanodata.csv")
lake_raw <- read.csv("/nfs/waterwomenfisheries-data/kisumubay2_cyanos.csv")

littoral_raw$site <- gsub("\\s", "", littoral_raw$site)

littoral_WQ <- littoral_raw %>%
  filter(site %in% locations)
params <- "ecol|sec|coli|chlo|nitra|SRP"

litt.col <- grep(params, names(littoral_raw), value=TRUE, 
             ignore.case = T)
lake.col <- grep(params, names(lake_raw), value=TRUE,
             ignore.case = T)

lake_small <- lake_raw %>%
  select(Date, Location, Depth, lake.col) %>%
  filter(Depth != "Integrated") %>%
  select(-Depth)
names(lake_small)[3:8] <- c("SRP", "NO3", "ChlA", "Colif", 
                            "EColi", "Secchi")
lake_small$site <- as.character(lake_small$Location)

lake_all_raw <- littoral_raw %>%
  select(site, month, litt.col) 
names(lake_all_raw)[3:7] <- c("ChlA", "NO3", "SRP", "Colif", "EColi")

cdata <- lake_all_raw %>%
  full_join(lake_small) %>%
  filter(site != "")
library("PerformanceAnalytics")
my_data <- cdata[,-c(1:2,8:9)]
log_my_data <- log10(my_data+1)

chart.Correlation(log_my_data, histogram=TRUE, pch=19)

```


## Q2. How do perceptions of lake “water quality” influence fishermen behavior?

```{r echo=FALSE, warning=FALSE, cache=TRUE, message=FALSE, out.width = '80%'}
survey_Fisher_All<- read.csv("data_out/survey_FisherWQperception_All.csv")
p<- ggplot(survey_Fisher_All) + geom_bar(aes(x=beach.name, na.rm = TRUE, fill= choice.fishing.area)) 
p + labs(x="Fishing village community",y="counts (selection of fishing sites)") + 
  theme_classic()+ 
  theme(axis.text.x = element_text(angle = 60, hjust = 1))
```

## Lots more to do...

## Deeper exploration of survey information

Creation of a shiny app

## Limitations of our current data

- Additional water quality data options

    + Water quality monitoring from colleagues (KMFRI)
    + Remote sensing data
    

- Addition of broader socio-ecological datasets

    + Community population size
    + Human health metrics
    + Other datasets?

## Maybe a Pursuit??


