---
title: "Water Women and Fisheries SESYNC"
output: ioslides_presentation
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Water, Women, and Fisheries

Addressing two ecological realities impacting human health at the world’s largest tropical lake, Lake Victoria

- Jessica Corman
- Amber Roegner

## Lake Victoria

- Largest tropical lake (68,800 km2)
- Eutrophic
- Largest freshwater fishery (>500,000 tonnes yr-1)

## Research Questions
- Q1: Do perceptions of lake “water quality” correlate with ecological trends (spatial, variability,
temporal)?

- Q2: Do perceptions of lake “water quality” influence behavior or decision-making process
about ecosystem services? 

- Q3: Does intervention X change “water quality” locally (overall or variability in water quality)? If so, how?

- Q4: Does intervention X change individual perception of water quality? Does intervention X
change fisher or household behavior or decision-making process?

## Study sites in Winam Gulf

```{r echo=FALSE, warning=FALSE, message=FALSE, cache=TRUE}
source("code/DataPrep_SiteInfo.R")

library(ggmap)

# Map of Winam Gulf with all sites
bbox <- c(left=34,bottom=-0.6,right=34.9,top=0)
g <- ggmap(get_stamenmap(bbox, zoom=11, maptype="toner-lite"))
g +  geom_point(data=Lake_Sites,
                aes(x=Longitude, y=Latitude, color=Location), size=3, alpha=0.95) +
  geom_point(data=Communities,
             aes(x=Longitude, y=Latitude), alpha=0.5, color="black") +
  geom_hline(yintercept = 0, color = "black") +
  geom_vline(xintercept = 34.9, color="black") +
  theme_classic(12) 
```


## How do perceptions of lake “water quality” correlate with ecological trends?

- Comparison of surveys from communities with corresponding lake water quality information

## Preliminary exploration

```{r echo=FALSE, warning=FALSE, cache=TRUE, message=FALSE}
source(file = 'code/DataAnalysis_CorrelationWQbySurveys.R')
```

## How do perceptions of lake “water quality” influence behavior or decision-making process about ecosystem services?

```{r pressure}
plot(pressure)
```

